The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-01-14 article/article.tex
change layout

\documentclass{acm_proc_article-sp}

\usepackage{comment}
\usepackage{hyperref}
\usepackage{amssymb}

@@

\title{The Power of Two Random Choices}
\subtitle{\large A follow up seminar to the lecture ``Parallel Algorithms''\\ by Jesper Larsson Tr\"aff and Francesco Versaci, 2012 winter term at TU Wien.}

\numberofauthors{1}
\author{
\alignauthor
Martin Kalany\\
       0825673
}    
\date{\today}

>>>>

\documentclass[a4paper,10pt, twocolumn]{article}
\usepackage[utf8]{inputenc}

\usepackage{comment}
\usepackage{hyperref}
\usepackage{amssymb}
%page boarders
\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}
\usepackage{enumitem}
\usepackage{float}
\floatstyle{plaintop}

\restylefloat{table}
\setlist{nolistsep}

@@

\title{The Power of Two Random Choices\\ 
\large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}}
\author{Martin Kalany, 0825673}
